Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-15 Grassmannian_cells.tex

\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}\label{sec:bb}
The aim of Section~\ref{torusaction} is to define a $\CC^*$-action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its $\CC^*$ fixed points.
\begin{theorem}
  \label{thm:bb}
  \cite[Section 4]{bb}
  Each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine bundle.
  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$.
  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
\end{theorem}

@@

The 2-quiver $\cQ_3^{[r]}$ associated to $\tilde P_3^{[r]}$ has underlying quiver $Q_3^{[r]}:=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=r+1}^{n-1} Q_{2,i}$.
Note that we are not taking this union as subquivers of $\widetilde{K(n)}$, in particular each quiver $Q_{2,i}$ has a vertex which can be associated to $(1,e)$ in $\widetilde{K(n)}$ but these are not identified in the quiver $Q_3^{[r]}$. 
For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\implies\Gamma_s(2)$ of $\cQ_3^{[r]}$ given by $\Gamma_s(1)=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=s+1}^{n-1} Q_{2,i}$ with $\Gamma_s(2)\subset Q_{2,s}$ the subquiver $(2,\alpha_s^{-1})\xrightarrow{\alpha_s} (1,e)$.
By Lemma~\ref{lem:2equivalence}, we obtain an equivalent 2-quiver by replacing each $\Gamma_s(2)$ above with the corresponding sink $(1,e)$ taken as a vertex of $Q_{2,s}$.
By a slight abuse of notation, below we will let $\cQ_3^{[r]}$ denote this equivalent 2-quiver.
Then $\cQ_3^{[r]}$ can be found as a sub-2-quiver of $\cQ_3$ which is constructed recursively by connecting $\cQ_3^{[i]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
\[
\begin{tikzpicture}[scale=1.35]
  \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} +(0.1,-1.3) node {\footnotesize$\mathcal Q_3$}; 
  \draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
  \draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
  \draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
  \draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

@@

%\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
\draw[-implies,double equal sign distance,red] (Q0)--(J33) node[pos=.5,above] {\scriptsize $b$};
\draw[-implies,double equal sign distance,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
\draw[-implies,double equal sign distance,red] (Q2)--(J11) node[pos=.5,above] {´};
\end{tikzpicture}
\\

The one of $\tilde P_4$ is given by:\\

@@

\end{tikzpicture}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Compatible Pairs}
For $m\ge1$, let $D_m$ denote the maximal Dyck path in the lattice rectangle with corner vertices $(0,0)$ and $(u_m,u_{m-1})$.  
More precisely, $D_m$ is the lattice path which begins at $(0,0)$, takes East and North steps to end at $(u_m,u_{m-1})$, and never passes above the main diagonal joining $(0,0)$ and $(u_m,u_{m-1})$.  
It is maximal in the sense that any lattice point lying strictly above $D_m$ also lies above the main diagonal.  
The maximal Dyck paths $D_m$, $m\ge1$, exhibit the following recursive structure.
In what follows we assume $n\ge2$.
\begin{theorem}
  \cite[Corollary 2.4]{rupel}
  \label{th:dyck path recursion}
  For $n\ge2$, the maximal Dyck path $D_m$, $m\ge1$, can be constructed recursively as follows:
  \begin{enumerate}
    \item $D_1$ consists of a single horizontal edge;
    \item $D_2$ consists of $n$ consecutive horizontal edges followed by a vertical edge;
    \item $D_m$, $m\ge3$, consists of $n-1$ copies of $D_{m-1}$ followed by a copy of $D_{m-1}$ with its first $D_{m-2}$ removed.
  \end{enumerate}
\end{theorem}

We obtain the following as an immediate consequence.
\begin{corollary}
  \label{cor:short hooks}
  Inside $D_m$, $m\ge2$, there are precisely $u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges, all other vertical egdes are immediately preceded by exactly $n$ horizontal edges.
\end{corollary}
\begin{proof}
  We work by induction on $m\ge2$.
  The cases $m=2,3$ are immediate from Theorem~\ref{th:dyck path recursion} parts (2) and (3).
  For $m\ge4$, part (3) of Theorem~\ref{th:dyck path recursion} shows by induction that there are $(n-1)u_{m-3}+(u_{m-3}-u_{m-4})=u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
\end{proof}

@@

To describe precisely when a piecewise compatible pair $(S_H,S_V)$ is compatible we need more notation.
For a horizontal edge $h\in H_{m+1}$ and a subset $S_H\subset H_{m+1}$, write $D(h;S_H)=he$ for the shortest subpath of $D_{m+1}$ for which $|he\cap V_{m+1}|=n|he\cap S_H|$, if no such subpath exists we set $D(h;S_H)=hv_{u_m}$.
The subpath $D(h;S_H)$ is called the \emph{local shadow path} of $h$ with respect to $S_H$.
Similarly, for a vertical edge $v\in V_{m+1}$ and a subset $S_V\subset V_{m+1}$, the \emph{local shadow path} of $v$ with repect to $S_V$ is $D(v;S_V)=ev$ for the shortest subpath of $D_{m+1}$ for which $|ev\cap H_{m+1}|=n|ev\cap S_V|$ and we take $D(v;S_V)=h_1v$ if there does not exist such an edge $e$.
\begin{definition}
  \cite[Definition 3.17]{rupel}
  A horizontal edge $h_i\in H_{m+1}$, $m\ge2$, is called \emph{blocking} for a subset $S_H\subset H_{m+1}$ if $D(h_i;S_H)=h_iv_{u_m}$ and $h_i$ is furthest to the right with this property, i.e.\ the index $i$ is maximal.

@@

The results of \cite{rupel} provide a stronger statement than Theorem~\ref{th:combinatorial euler}.
Indeed, the compatible pairs are shown to compute the counting polynomials of these quiver Grassmannians $\Gr_\bfe(P_{m+1})$ over a finite field (these coincide with their Poincar\'e polynomials in this case).  
We conjecture that the torus action on $\Gr_\bfe(P_{m+1})$ can be chosen to provide a geometric explaination of this result.
\begin{conjecture}
  \label{conj:cell dimensions}
  For $m\ge1$ and $V\in\Gr(H_m)$ or $V=0$, there exists a torus action on $\Gr_\bfe(P_{m+1}^V)$ such that the dimension of the cell labeled by a compatible pair $(S_H,S_V)$ in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$, is given by $\overline{\gamma}_{S_H,S_V}=\sum\limits_{e<e'\in E_{m+1}^{[r]}}\overline{\gamma}_\omega(e,e')$ for
  \begin{equation*}
    \overline{\gamma}_\omega(e,e')=\begin{cases}
      -n & \text{if $e\in S_H$ and $e'\in S_V$;}\\ 
      1 & \text{if $e\in S_H$ and $e'\in H_{m+1}^{[r]}\setminus S_H$;}\\ 
      1 & \text{if $e\in V_{m+1}^{[r]}\setminus S_V$ and $e'\in S_V$;}\\ 
      0 & \text{otherwise.}\\ 
    \end{cases}
  \end{equation*}
\end{conjecture}

@@

\bibitem{ass} 
  I.~Assem, D.~Simson, A.~Skowronski: Elements of the Representation Theory of Associative Algebras. Cambridge University Press, Cambridge 2007.
\bibitem{ars} 
  M.~Auslander, I.~Reiten, S.~O.~Smalo: Representation theory of Artin algebras {\bf 36}. Cambridge University Press, Cambridge 1997.
\bibitem{bb} 
  A.~Bia\l{}ynicki-Birula: Some theorems on actions of algebraic groups. Annals of Mathematics \textbf{98}, 480-497 (1973).
\bibitem{bgp} 
  I.~N.~Bernstein, I.~M.~Gelfand, V.~A.~Ponomarev: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
\bibitem{brenner-butler} 
  S.~Benner, M.~C.~R.~Butler: The equivalence of certain functors occuring in the representation theory of artin algebras and species. Journal of the London Mathematical Society \textbf{2}(1), 183-187 (1976).
\bibitem{cc} 
  P.~Caldero, F.~Chapoton: Cluster algebras as {H}all algebras of quiver representations. Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).
\bibitem{ck} 
  P.~Caldero, B.~Keller: From triangulated categories to cluster algebras II.  Annales Scientifique de l'Ecole Normale Superi\'{e}ure (4) \textbf{39} (6), 983-1009 (2006).
\bibitem{ce} 
  G.~Cerulli Irelli, F.~Esposito: Geometry of quiver Grassmannians of Kronecker type and applications to cluster algebras. Algebra \&  Number Theory \textbf{5}(6), 777-801 (2011).
\bibitem{cefr} 
  G.~Cerulli Irelli, F.~Esposito, H.~Franzen, M.~Reineke: Topology of Quiver Grassmannians. Preprint 2018.
\bibitem{cr} 
  P.~Caldero, M.~Reineke: On the quiver Grassmannian in the acyclic case. Journal of Pure and Applied Algebra \textbf{212}(11), 2369-2380 (2008).
%\bibitem{cj} Crawley-Boevey, W., Jensen, Bernt Tore: A note on sub-bundles of vector bundles. Glasgow Mathematical Journal \textbf{48}, 459-462 (2006).
\bibitem{gab} 
  P.~Gabriel: The universal cover of a finite-dimensional algebra. Representations of algebras. Lecture Notes in Mathematics {\bf 903}, 68-105 (1981).
%\bibitem{hr} 
 % D.~Happel, C.~M.~Ringel: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}(2), 399-443 (1982).
\bibitem{llz} 
  K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Mathematica \textbf{20}(1), 57-82 (2014).
\bibitem{lw} 
  O.~Lorscheid, T.~Weist: Representation type via Euler characteristics and singularities of quiver Grassmannians. Preprint 2017, arXiv:1706.00860.
\bibitem{rin1} 
  C.~M.~Ringel. Exceptional modules are tree modules. Linear algebra and its Applications \textbf{275/276}, 471-493 (1998).
%\bibitem{rin} 
 % C.~M.~Ringel: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}(3), 465-479 (1980).
%\bibitem{mats} Matsumura, H.: Commutative ring theory. 
\bibitem{rupel} 
  D.~Rupel: Rank Two Non-Commutative Laurent Phenomenon and Pseudo-Positivity. Preprint 2017, arXiv:1707.02696.
\bibitem{sch} 
  A.~Schofield: General representations of quivers. Proceedings of the London Mathematical Society (3) \textbf{65}(1), 46-64 (1992).
\bibitem{wei} 
  T.~Weist: Localization of quiver moduli spaces. Representation Theory \textbf{17}(13), 382-425 (2013).
%\bibitem{wei2} 
 % T.~Weist: Tree modules. Bulletin of the London Mathematical Society \textbf{44}(5), 882-898 (2012).
%\bibitem{wei3} Weist, T.: On the recursive construction of indecomposable quiver representations. Journal of Algebra \textbf{443}, 49-74 (2015).
\end{thebibliography}

>>>>

\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}\label{sec:bb}
The aim of Section~\ref{torusaction} is to define a $\CC^*$-action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its $\CC^*$ fixed points (see \cite[Section 4]{bb} or \cite[Section 4]{ca}).
\begin{theorem}
  \label{thm:bb}
  Let $X$ be a smooth projective complex variety with a $\C^\ast$-action.
  Then each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine bundle.
  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$, where we can choose an ordering such that $\coprod_{i=1}^s\Att(C_i)$ is closed for $1\leq s\leq r$.
  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
\end{theorem}

@@

The 2-quiver $\cQ_3^{[r]}$ associated to $\tilde P_3^{[r]}$ has underlying quiver $Q_3^{[r]}:=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=r+1}^{n-1} Q_{2,i}$.
Note that we are not taking this union as subquivers of $\widetilde{K(n)}$, in particular each quiver $Q_{2,i}$ has a vertex which can be associated to $(1,e)$ in $\widetilde{K(n)}$ but these are not identified in the quiver $Q_3^{[r]}$. 
For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\implies\Gamma_s(2)$ of $\cQ_3^{[r]}$ given by $\Gamma_s(1)=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=s+1}^{n-1} Q_{2,i}$ with $\Gamma_s(2)\subset Q_{2,s}$ the subquiver $(2,\alpha_s^{-1})\xrightarrow{\alpha_s} (1,e)$.
By Lemma~\ref{lem:2equivalence}, we obtain an equivalent 2-quiver by replacing each $\Gamma_s(2)$ above with the corresponding sink $(1,e)$ taken as a vertex of $Q_{2,s}$.
By a slight abuse of notation, below we will let $\cQ_3^{[r]}$ denote this equivalent 2-quiver.
Then $\cQ_3^{[r]}$ can be found as a sub-2-quiver of $\cQ_3$ which is constructed recursively by connecting $\cQ_3^{[i]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \bigskip
\[
\begin{tikzpicture}[scale=1.35]
  \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} +(0.1,-1.3) node {\footnotesize$\mathcal Q_3$}; 
  \draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
  \draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
  \draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
  \draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

@@

%\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
\draw[-implies,double equal sign distance,red] (Q0)--(J33) node[pos=.5,above] {\scriptsize $b$};
\draw[-implies,double equal sign distance,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
\draw[-implies,double equal sign distance,red] (Q2)--(J11) node[pos=.5,above] {´};
\end{tikzpicture}
\bigskip

The one of $\tilde P_4$ is given by:\bigskip

@@

\end{tikzpicture}\bigskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Compatible Pairs}
For $m\ge1$, let $D_m$ denote the maximal Dyck path in the lattice rectangle with corner vertices $(0,0)$ and $(u_m,u_{m-1})$.  
More precisely, $D_m$ is the lattice path which begins at $(0,0)$, takes East and North steps to end at $(u_m,u_{m-1})$, and never passes above the main diagonal joining $(0,0)$ and $(u_m,u_{m-1})$.  
It is maximal in the sense that any lattice point lying strictly above $D_m$ also lies above the main diagonal.  
The maximal Dyck paths $D_m$, $m\ge1$, exhibit the following recursive structure.
In what follows we assume $n\ge2$.
\begin{theorem}
  \cite[Corollary 2.4]{rupel}
  \label{th:dyck path recursion}
  For $n\ge2$, the maximal Dyck path $D_m$, $m\ge1$, can be constructed recursively as follows:
  \begin{enumerate}
    \item $D_1$ consists of a single horizontal edge;
    \item $D_2$ consists of $n$ consecutive horizontal edges followed by a vertical edge;
    \item $D_m$, $m\ge3$, consists of $n-1$ copies of $D_{m-1}$ followed by a copy of $D_{m-1}$ with its first $D_{m-2}$ removed.
  \end{enumerate}
\end{theorem}

We obtain the following as an immediate consequence.
\begin{corollary}
  \label{cor:short hooks}
  Inside $D_m$, $m\ge2$, there are precisely $u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges, all other vertical edges are immediately preceded by exactly $n$ horizontal edges.
\end{corollary}
\begin{proof}
  We work by induction on $m\ge2$.
  The cases $m=2,3$ are immediate from Theorem~\ref{th:dyck path recursion} parts (2) and (3).
  For $m\ge4$, part (3) of Theorem~\ref{th:dyck path recursion} shows by induction that there are $(n-1)u_{m-3}+(u_{m-3}-u_{m-4})=u_{m-2}$ vertical edges which are immediately preceded by exactly $n-1$ horizontal edges.
\end{proof}

@@

To describe precisely when a piecewise compatible pair $(S_H,S_V)$ is compatible we need more notation.
For a horizontal edge $h\in H_{m+1}$ and a subset $S_H\subset H_{m+1}$, write $D(h;S_H)=he$ for the shortest subpath of $D_{m+1}$ for which $|he\cap V_{m+1}|=n|he\cap S_H|$, if no such subpath exists we set $D(h;S_H)=hv_{u_m}$.
The subpath $D(h;S_H)$ is called the \emph{local shadow path} of $h$ with respect to $S_H$.
Similarly, for a vertical edge $v\in V_{m+1}$ and a subset $S_V\subset V_{m+1}$, the \emph{local shadow path} of $v$ with respect to $S_V$ is $D(v;S_V)=ev$ for the shortest subpath of $D_{m+1}$ for which $|ev\cap H_{m+1}|=n|ev\cap S_V|$ and we take $D(v;S_V)=h_1v$ if there does not exist such an edge $e$.
\begin{definition}
  \cite[Definition 3.17]{rupel}
  A horizontal edge $h_i\in H_{m+1}$, $m\ge2$, is called \emph{blocking} for a subset $S_H\subset H_{m+1}$ if $D(h_i;S_H)=h_iv_{u_m}$ and $h_i$ is furthest to the right with this property, i.e.\ the index $i$ is maximal.

@@

The results of \cite{rupel} provide a stronger statement than Theorem~\ref{th:combinatorial euler}.
Indeed, the compatible pairs are shown to compute the counting polynomials of these quiver Grassmannians $\Gr_\bfe(P_{m+1})$ over a finite field (these coincide with their Poincar\'e polynomials in this case).  
We conjecture that the torus action on $\Gr_\bfe(P_{m+1})$ can be chosen to provide a geometric explanation of this result.
\begin{conjecture}
  \label{conj:cell dimensions}
  For $m\ge1$ and $V\in\Gr(H_m)$ or $V=0$, there exists a torus action on $\Gr_\bfe(P_{m+1}^V)$ such that the dimension of the cell labeled by a compatible pair $(S_H,S_V)$ in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$, is given by $\overline{\gamma}_{S_H,S_V}=\sum\limits_{e<e'\in E_{m+1}^{[r]}}\overline{\gamma}_\omega(e,e')$ for
  \begin{equation*}
    \overline{\gamma}_\omega(e,e')=\begin{cases}
      -n & \text{if $e\in S_H$ and $e'\in S_V$;}\\ 
      1 & \text{if $e\in S_H$ and $e'\in H_{m+1}^{[r]}\setminus S_H$;}\\ 
      1 & \text{if $e\in V_{m+1}^{[r]}\setminus S_V$ and $e'\in S_V$;}\\ 
      0 & \text{otherwise.}\\ 
    \end{cases}
  \end{equation*}
\end{conjecture}

@@

\bibitem{ass} 
  I.~Assem, D.~Simson, A.~Skowronski: Elements of the Representation Theory of Associative Algebras. Cambridge University Press, Cambridge 2007.
\bibitem{ars} 
  M.~Auslander, I.~Reiten, S.~O.~Smalo: Representation theory of Artin algebras {\bf 36}. Cambridge University Press, Cambridge 1997.
\bibitem{bb} 
  A.~Bia\l{}ynicki-Birula: Some theorems on actions of algebraic groups. Annals of Mathematics \textbf{98}, 480-497 (1973).
\bibitem{bgp} 
  I.~N.~Bernstein, I.~M.~Gelfand, V.~A.~Ponomarev: Coxeter functors, and Gabriel's theorem. Russian Mathematical Surveys \textbf{28}(2), 17-32 (1973).
\bibitem{brenner-butler} 
  S.~Brenner, M.~C.~R.~Butler: The equivalence of certain functors occuing in the representation theory of artin algebras and species. Journal of the London Mathematical Society \textbf{2}(1), 183-187 (1976).
\bibitem{cc} 
  P.~Caldero, F.~Chapoton: Cluster algebras as {H}all algebras of quiver representations. Commentarii Mathematici Helvetici \textbf{81}(3), 595-616 (2006).
\bibitem{ck} 
  P.~Caldero, B.~Keller: From triangulated categories to cluster algebras II.  Annales Scientifique de l'Ecole Normale Superi\'{e}ure (4) \textbf{39} (6), 983-1009 (2006).
\bibitem{ca}	J.B.~Carrell: Torus actions and cohomology. Algebraic quotients. Torus actions and cohomology. The adjoint representation and the adjoint action, 83-158. Encyclopaedia Mathematical Science \textbf{131}, Invariant Theory and Algebraic
Transformation Groups, Springer, Berlin, 2002.
\bibitem{ce} 
  G.~Cerulli Irelli, F.~Esposito: Geometry of quiver Grassmannians of Kronecker type and applications to cluster algebras. Algebra \&  Number Theory \textbf{5}(6), 777-801 (2011).
\bibitem{cefr} 
  G.~Cerulli Irelli, F.~Esposito, H.~Franzen, M.~Reineke: Topology of Quiver Grassmannians. Preprint 2018.
\bibitem{cr} 
  P.~Caldero, M.~Reineke: On the quiver Grassmannian in the acyclic case. Journal of Pure and Applied Algebra \textbf{212}(11), 2369-2380 (2008).
%\bibitem{cj} Crawley-Boevey, W., Jensen, Bernt Tore: A note on sub-bundles of vector bundles. Glasgow Mathematical Journal \textbf{48}, 459-462 (2006).
\bibitem{gab} 
  P.~Gabriel: The universal cover of a finite-dimensional algebra. Representations of algebras. Lecture Notes in Mathematics {\bf 903}, 68-105 (1981).
%\bibitem{hr} 
 % D.~Happel, C.~M.~Ringel: Tilted Algebras. Transactions of the American Mathematical Society {\bf 274}(2), 399-443 (1982).
\bibitem{llz} 
  K.~Lee, L.~Li, A.~Zelevinsky: Greedy elements in rank 2 cluster algebras. Selecta Mathematica \textbf{20}(1), 57-82 (2014).
\bibitem{lw} 
  O.~Lorscheid, T.~Weist: Representation type via Euler characteristics and singularities of quiver Grassmannians. Preprint 2017, arXiv:1706.00860.
\bibitem{rin1} 
  C.~M.~Ringel. Exceptional modules are tree modules. Linear algebra and its Applications \textbf{275/276}, 471-493 (1998).
%\bibitem{rin} 
 % C.~M.~Ringel: Reflection functors for hereditary algebras. Journal of the London Mathematical Society (2) {\bf 21}(3), 465-479 (1980).
%\bibitem{mats} Matsumura, H.: Commutative ring theory. 
\bibitem{rupel} 
  D.~Rupel: Rank Two Non-Commutative Laurent Phenomenon and Pseudo-Positivity. Preprint 2017, arXiv:1707.02696.
\bibitem{sch} 
  A.~Schofield: General representations of quivers. Proceedings of the London Mathematical Society (3) \textbf{65}(1), 46-64 (1992).
\bibitem{wei} 
  T.~Weist: Localization of quiver moduli spaces. Representation Theory \textbf{17}(13), 382-425 (2013).
%\bibitem{wei2} 
 % T.~Weist: Tree modules. Bulletin of the London Mathematical Society \textbf{44}(5), 882-898 (2012).
%\bibitem{wei3} Weist, T.: On the recursive construction of indecomposable quiver representations. Journal of Algebra \textbf{443}, 49-74 (2015).
\end{thebibliography}
